---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(here)
library(googlesheets)
library(knitr) # brings kable() into namespace
library(kableExtra)
library(dplyr)
library(ggplot2)
library(scales)
```


```{r, include = FALSE}
gs_auth(token = here::here("googlesheets_token.rds"))
gs_ls()
resbaz_url <- "https://docs.google.com/spreadsheets/d/1gSHnIzLs3gWXVGrIYrCpzqrCMAODYauada1xjeYhdxU"
(resbaz_sheet_info <- gs_url(resbaz_url))
resbaz <- gs_read(resbaz_sheet_info) %>% select(-2,-3)
names(resbaz) <-c("Time", "Institution", "Dept","Gender","Age","Career","Discipline","Day1WS", "Talks","Dietary","Capacity","Contact", "Day2WS")
```

Resbaz Numbers
=====================================

Column {data-width=650}
-----------------------------------------------------------------------

### Workshop choice by day

```{r}
Workshops <- tibble(Time = rep(resbaz$Time, 2), workshop = c(resbaz$Day1WS, resbaz$Day2WS), day = c(rep(1,length(resbaz$Day1WS) ), rep(2, length(resbaz$Day2WS))))


p1<- Workshops %>% ggplot(aes(workshop, fill = workshop)) + geom_bar() + theme_bw() + theme(axis.text.x = element_text(angle = 60, hjust = 1)) + geom_hline(yintercept = 60) + geom_hline(yintercept = 40, lty= 'dashed') + theme(axis.text.x = element_blank(), legend.position = "bottom", legend.title = element_blank()) +  geom_text(aes(label=..count..),stat="count", position=position_dodge(0.9),vjust=-0.2) + facet_grid(day~.) + guides(fill = guide_legend(ncol = 3,nrow = 3, title.position = 'top'))

p2 <- Workshops %>% filter(workshop != "I will not be attending the workshops") %>% group_by(day) %>% tally()%>% ggplot(., aes(x = factor(day), y = n, fill = factor(day))) + geom_bar(stat = 'identity') + theme_bw() + geom_hline(yintercept = 140, colour = "red") + theme( axis.ticks.x = element_blank(), legend.position = 'none') + geom_text(aes(label = n, y=n),stat="identity", position=position_dodge(0.9),vjust=-0.2)

cowplot::plot_grid(p1,p2, ncol = 1, rel_heights = c(3,1))
```

Column {data-width=350}
-----------------------------------------------------------------------

### Total Registrants - Workshops (day 1 = `r Workshops %>% filter(workshop != "I will not be attending the workshops") %>% group_by(day) %>% tally() %>% filter(day == 1) %>% pull(n)`, day 2 = `r Workshops %>% filter(workshop != "I will not be attending the workshops") %>% group_by(day) %>% tally() %>% filter(day == 2) %>% pull(n)`)

```{r}



p2 <- Workshops %>% mutate(date = lubridate::mdy_hms(Time), attend = 1)  %>% group_by(day, workshop) %>% mutate(remain = 60 - cumsum(attend)+1, sum_attend = cumsum(attend))%>% ggplot(., aes(x = date,y = sum_attend, by = workshop, colour = workshop)) + geom_line() +  theme_bw() + geom_hline(yintercept = 60, colour = "red") + scale_y_continuous(limits = c(0, 60)) + facet_grid(day~.) + geom_hline(yintercept = 40, lty = 'dashed')

p2
```

### Attend Talks (n = `r resbaz %>% mutate(attend = if_else(Talks == "I will attend the talks/demonstrations on July 6 .", 1, 0)) %>% summarise(sum(attend))`)

```{r}
resbaz %>% mutate(attend = if_else(Talks == "I will attend the talks/demonstrations on July 6 .", 1, 0)) %>% mutate(date = lubridate::mdy_hms(Time)) %>% mutate(remain = 400 - cumsum(attend)+1)%>% ggplot(., aes(x = date,y = remain)) + geom_line(lty = "dashed") + geom_line(aes(y = cumsum(attend))) +  theme_bw() + geom_hline(yintercept = 400, colour = "red") + scale_y_continuous(limits = c(0, 400))
```

Backgrounds
==================

Column {data-width=650}
-----------------------------------------------------------------------

### Discipline

```{r}
resbaz %>% ggplot(., aes(x = Discipline, fill = Discipline)) + geom_bar() + theme_bw()+ theme(axis.text.x = element_blank(), legend.position = 'bottom') + guides(fill = guide_legend(ncol = 2,nrow = 5, title.position = 'top'))
```

### Career Stage

```{r, fig.width=6}
resbaz %>% ggplot(., aes(x = Career, fill = Career)) + geom_bar() + theme_bw()+ theme(axis.text.x = element_blank(),legend.position = 'bottom') + guides(fill = guide_legend(ncol = 2,nrow = 4, title.position = 'top'))
```


Column {data-width=350}
-----------------------------

### Age

```{r}
resbaz %>% ggplot(., aes(x = Age, fill = Age)) + geom_bar() + theme_bw()
```

### Gender

```{r}
resbaz %>% ggplot(., aes(x = Gender, fill = Gender)) + geom_bar() + theme_bw() + theme(legend.position = 'none')
```


```{r}
words <- stringr::str_split(resbaz$Dept, " ") %>% purrr::flatten_chr() %>% unique() %>% stringr::str_to_lower()
words <- words[!words %in% c("of", "&", "and", "school", 'dunedin', 'services', "department" ) ]
```

